%-------------------------
% Resume in Latex
% Author : Bhavesh Chhimwal
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% (kept commented intentionally)

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------- Achievement commands (matched spacing) --------
\newcommand{\achievementItemListStart}{\begin{itemize}}
\newcommand{\achievementItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\achievementItem}[1]{
  \item\small{
    {#1 \vspace{-5pt}}
  }
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textbf{Bhavesh Chhimwal}} \\[5pt]
    \href{mailto:bhaveshchhimwal01@gmail.com}{bhaveshchhimwal01@gmail.com} \\[5pt]
    \href{https://www.linkedin.com/in/bhavesh-chhimwal/}{LinkedIn} $|$
    \href{https://www.codechef.com/users/conficker_404}{CodeChef} $|$
    \href{https://leetcode.com/u/conficker_404/}{LeetCode} $|$
    \href{https://github.com/bhaveshchhimwal}{GitHub} $|$
    \href{https://bhaveshchhimwal.netlify.app/}{Portfolio}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Panjab University, Chandigarh}{2023 -- 2027}
      {Bachelor of Engineering in Information Technology}{CGPA: 7.3/10}
    \resumeSubheading
      {Mother’s Glory Public School, Ramnagar}{2019 -- 2023}
      {Senior Secondary Education}{Grade: 88.8\%}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Intern}{June 2025 -- July 2025}
      {Avayo Technologies}{Jaipur, India}
      \resumeItemListStart
       \resumeItem{Developed and maintained scalable \textbf{RESTful APIs} using \textbf{Node.js} and \textbf{Express.js}, enhancing backend performance, scalability, and overall system responsiveness.}
       \resumeItem{Implemented secure authentication and authorization using \textbf{JWT} and \textbf{OAuth}, strengthening data protection and preventing unauthorized access.}
       \resumeItem{Integrated secure \textbf{payment gateways} and optimized transaction handling to ensure reliable online payments.}
       \resumeItem{Collaborated with \textbf{frontend teams} to ensure smooth \textbf{end-to-end API integration}, improving data consistency and reducing integration overhead.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{NexChat} $|$ \href{https://nexchat44.onrender.com/}{\underline{Live Demo}}}{\emph{MongoDB, Express.js, React.js, Node.js, Socket.IO}}
    \resumeItemListStart
      \resumeItem{Built a \textbf{real-time CRUD chat application} with \textbf{WebSockets} for instant, bidirectional communication.}
      \resumeItem{Implemented secure authentication and authorization using \textbf{JWT} and \textbf{bcrypt} for data protection.}
      \resumeItem{Integrated an \textbf{AI assistant} using the \textbf{Google Gemini API} to provide intelligent chat responses.}
      \resumeItem{Utilized \textbf{MongoDB} as the backend database and \textbf{Cloudinary} for storing and sharing media files.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{PopIn} $|$ \href{https://github.com/...}{\underline{Live Demo}}}{\emph{Express.js, React.js, Node.js, Stripe API}}
    \resumeItemListStart
      \resumeItem{Developed a full-stack web application allowing organizers to list events and users to securely purchase tickets.}
      \resumeItem{Implemented secure authentication using \textbf{Firebase Google OAuth} and \textbf{JWT}, enabling seamless user login.}
      \resumeItem{Designed \textbf{MongoDB schemas} to efficiently manage \textbf{users, events, tickets, and transactions}.}
      \resumeItem{Integrated \textbf{Cloudinary} for efficient media storage and the \textbf{Stripe API} to implement a secure payment gateway.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Blog API} $|$ \href{https://github.com/...}{\underline{GitHub}}}{\emph{Node.js, Express.js, MongoDB}}
    \resumeItemListStart
      \resumeItem{Designed and developed a \textbf{RESTful API} to manage posts, users, and comments.}
      \resumeItem{Implemented \textbf{JWT-based authentication} and role-based authorization for secure access control.}
      \resumeItem{Integrated \textbf{Mongoose ODM} for schema validation, relational data handling, and efficient database queries.}
      \resumeItem{Added \textbf{CRUD functionality} with pagination and filtering to optimize API performance and scalability.}
      \resumeItem{Tested endpoints using \textbf{Postman} to ensure reliability and performance validation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\achievementItemListStart
    \achievementItem{Achieved \textbf{2 stars} on CodeChef with a maximum rating of \textbf{1465}.}
    \achievementItem{Secured a \textbf{Global Rank} of \textbf{314} out of \textbf{35,792} participants in CodeChef Starters 172 (Div-4).}
    \achievementItem{Secured a \textbf{Global Rank} of \textbf{5533} out of \textbf{13,779} participants in the \textbf{\href{https://www.facebook.com/codingcompetitions/hacker-cup/2025/certificate/921287033136593}{Meta Hacker Cup 2025}}.}
    \achievementItem{Achieved a maximum rating of \textbf{1566} on LeetCode, ranking in the \textbf{top 28\%} of global users.}
\achievementItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, HTML, CSS, JavaScript, Python, SQL} \\
     \textbf{Libraries \& Frameworks}{: React.js, Node.js, Express.js, MongoDB, Firebase} \\
     \textbf{Relevant Coursework}{: OOP, Data Structures, Algorithms, OS, DBMS} \\
     \textbf{Others}{: Git, GitHub, Postman}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
